---
title: "Kai_Brehm_Assignment_V"
author: "Kai Brehm"
date: "6 Februar 2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

I hereby assure that my submission is in line with the *Code of Conduct* outlined
on the lecture slides.

### General setup

Before I start the project, I clear my workspace and install (if necessary) and 
load the packages that are needed for the assignment.

```{r general, message=FALSE, warning=FALSE,results = 'hide'}
rm(list = ls())

if (!require("jsonlite")) install.packages("jsonlite")
if (!require("httr")) install.packages("httr")
if (!require("rlist")) install.packages("rlist")
if (!require("tidyverse")) install.packages("tidyverse")
if (!require("naniar")) install.packages("naniar")

library(jsonlite)
library(httr)
library(rlist)
library(tidyverse)
library(naniar)
setwd("C:/Users/Kai Brehm/Desktop/Uni/3. Semester/DSPM/Excercises/DSPM_Assignment_V")

```
### Exercise 1: Setting up a new GitHub repository
The GitHub repository for this assignment is located at: https://github.com/KaiBrehm/DSPM_Assignment_V.git

### Exercise 2: Getting to know the API
``` {r Excercise_2, warning=FALSE}
# load the API key:
source("api_key.R")

```

### Exercise 3: Interacting with the API - the basics
* *Perform a first GET request, that searches for event venues in Germany*
  *(countryCode = "DE"). Extract the content from the response object and*
  *inspect the resulting list. Describe what you can see*
  
``` {r Excercise_3_1, warning=FALSE}
APIcontent <- GET("https://app.ticketmaster.com/discovery/v2/venues", 
                  query = list(apikey = key,
                               countryCode = "DE")) %>%
              content()
```
The resulting list object contains the information for the german venues in the
first object``_embedded``. There, each element of the list ``venues``, contains the 
variables for each venue. 


* *Extract the name, the city, the postalCode and address, as well as the url and *
  *the longitude and latitude of the venues to a data frame.*
``` {r Excercise_3_2, warning=FALSE}

#create an empty datframe:
n <- length(APIcontent$`_embedded`$venues)
venue_data <- tibble(
  name  = character(n),
  city   = character(n),
  postalCode = character(n),
  address   = character(n),
  url = character(n),
  longitude = character(n),
  latitude = character(n),
 )
#extract the lists containing the venue information
venues <- APIcontent$`_embedded`$venues

# loop over the lists to extract the respective variables for each venue
for (i in 1:n) {
  
  if (is.null(venues[[i]]$name)) {venue_data[i, 1] <- "NA"} 
  else {venue_data[i, 1] <- venues[[i]]$name}
  
  if (is.null(venues[[i]]$city)) {venue_data[i, 2] <- "NA"} 
  else {venue_data[i, 2] <- venues[[i]]$city}
  
  if (is.null(venues[[i]]$postalCode)) {venue_data[i, 3] <- "NA"} 
  else {venue_data[i, 3] <- venues[[i]]$postalCode}
  
  if (is.null(venues[[i]]$address)) {venue_data[i, 4] <- "NA"} 
  else {venue_data[i, 4] <- venues[[i]]$address}
  
  if (is.null(venues[[i]]$url)) {venue_data[i, 5] <- "NA"} 
  else {venue_data[i, 5] <- venues[[i]]$url}
  
  if (is.null(venues[[i]]$location$longitude)) {venue_data[i, 6] <- "NA"} 
  else {venue_data[i, 6] <- venues[[i]]$location$longitude}
  
  if (is.null(venues[[i]]$location$latitude)) {venue_data[i, 7] <- "NA"} 
  else {venue_data[i, 7] <- venues[[i]]$location$latitude}
}
glimpse(venue_data)
```


### Exercise 4: Interacting with the API - advanced
* *Check the API documentation under the section Venue Search. How can you request*
  *the venues from the remaining results pages?*


``` {r Excercise_4, warning=FALSE}
total_pages <- APIcontent$page$totalPages-1
total_results <-APIcontent$page$totalElements

venue_data <- tibble(
  name  = character(total_results),
  city   = character(total_results),
  postalCode = character(total_results),
  address   = character(total_results),
  url = character(total_results),
  longitude = character(total_results),
  latitude = character(total_results),
)

for (p in 0:total_pages) {

  APIcontent <- GET("https://app.ticketmaster.com/discovery/v2/venues", 
                    query = list(apikey = key,
                                 countryCode = "DE",
                                 page = p)) %>%
                content()
  
  venues <- APIcontent$`_embedded`$venues

  n <- length(APIcontent$`_embedded`$venues)
  
  for (i in 1:n) {
    
    if (is.null(venues[[i]]$name)) {venue_data[(p)*20 + i,1] <- "NA"} 
    else {venue_data[(p)*20 + i,1] <- venues[[i]]$name}
    
    if (is.null(venues[[i]]$city)) {venue_data[(p)*20 + i,2] <- "NA"} 
    else {venue_data[(p)*20 + i,2] <- venues[[i]]$city}
    
    if (is.null(venues[[i]]$postalCode)) {venue_data[(p)*20 + i,3] <- "NA"} 
    else {venue_data[(p)*20 + i,3] <- venues[[i]]$postalCode}
    
    if (is.null(venues[[i]]$address$line1)) {venue_data[(p)*20 + i,4] <- "NA"} 
    else {venue_data[(p)*20 + i,4] <- venues[[i]]$address$line1}
    
    if (is.null(venues[[i]]$url)) {venue_data[(p)*20 + i,5] <- "NA"} 
    else {venue_data[(p)*20 + i,5] <- venues[[i]]$url}
    
    if (is.null(venues[[i]]$location$longitude)) {venue_data[(p)*20 + i,6] <- "NA"} 
    else {venue_data[(p)*20 + i,6] <- venues[[i]]$location$longitude}
    
    if (is.null(venues[[i]]$location$latitude)) {venue_data[(p)*20 + i,7] <- "NA"} 
    else {venue_data[(p)*20 + i,7] <- venues[[i]]$location$latitude}
  }
  
  Sys.sleep(0.5)
}

venue_data$longitude <- as.numeric(venue_data$longitude)
venue_data$latitude <- as.numeric(venue_data$latitude)

glimpse(venue_data)
```

### Exercise 5: Visualizing the extracted data
* *Produce a map of Germany with points indicating the event venues.*

``` {r Excercise_5, warning=FALSE}
# only include coordinates, which are really within German borders:
venue_data$longitude[venue_data$longitude<5.866944 | venue_data$longitude > 15.043611] <- NA
venue_data$latitude[venue_data$latitude<47.271679 | venue_data$latitude > 55.0846] <- NA


venue_data %>% 
      ggplot(aes(longitude,latitude)) +
        geom_polygon(
          aes(x = long, y = lat, group = group), data = map_data("world", region = "Germany"),
        fill = "grey90",color = "black") +
        geom_point()+
        theme_void() + coord_quickmap() +
        labs(title = "Event locations across Germany", caption = "Source: ticketmaster.com") +
        theme(title = element_text(size=8, face='bold'),
             plot.caption = element_text(face = "italic"))
```

### Exercise 6: Event locations in other countries
* *Repeat exercises 2 to 5 for another European country of your choice. (Netherlands)*

``` {r Excercise_6, warning=FALSE}
source("api_key.R")

APIcontent <- GET("https://app.ticketmaster.com/discovery/v2/venues", 
                  query = list(apikey = key,
                               countryCode = "NL")) %>%
              content()

n <- length(APIcontent$`_embedded`$venues)
venue_data <- tibble(
  name  = character(n),
  city   = character(n),
  postalCode = character(n),
  address   = character(n),
  url = character(n),
  longitude = character(n),
  latitude = character(n),
)

venues <- APIcontent$`_embedded`$venues

for (i in 1:n) {
  
  if (is.null(venues[[i]]$name)) {venue_data[i, 1] <- "NA"} 
  else {venue_data[i, 1] <- venues[[i]]$name}
  
  if (is.null(venues[[i]]$city)) {venue_data[i, 2] <- "NA"} 
  else {venue_data[i, 2] <- venues[[i]]$city}
  
  if (is.null(venues[[i]]$postalCode)) {venue_data[i, 3] <- "NA"} 
  else {venue_data[i, 3] <- venues[[i]]$postalCode}
  
  if (is.null(venues[[i]]$address)) {venue_data[i, 4] <- "NA"} 
  else {venue_data[i, 4] <- venues[[i]]$address}
  
  if (is.null(venues[[i]]$url)) {venue_data[i, 5] <- "NA"} 
  else {venue_data[i, 5] <- venues[[i]]$url}
  
  if (is.null(venues[[i]]$location$longitude)) {venue_data[i, 6] <- "NA"} 
  else {venue_data[i, 6] <- venues[[i]]$location$longitude}
  
  if (is.null(venues[[i]]$location$latitude)) {venue_data[i, 7] <- "NA"} 
  else {venue_data[i, 7] <- venues[[i]]$location$latitude}
}

total_pages <- APIcontent$page$totalPages-1
total_results <-APIcontent$page$totalElements

venue_data <- tibble(
  name  = character(total_results),
  city   = character(total_results),
  postalCode = character(total_results),
  address   = character(total_results),
  url = character(total_results),
  longitude = character(total_results),
  latitude = character(total_results),
)

for (p in 0:total_pages) {
  
  APIcontent <- GET("https://app.ticketmaster.com/discovery/v2/venues", 
                    query = list(apikey = key,
                                 countryCode = "NL",
                                 page = p)) %>%
                content()
  
  venues <- APIcontent$`_embedded`$venues
  
  n <- length(APIcontent$`_embedded`$venues)
  
  for (i in 1:n) {
    
    if (is.null(venues[[i]]$name)) {venue_data[(p)*20 + i,1] <- "NA"} 
    else {venue_data[(p)*20 + i,1] <- venues[[i]]$name}
    
    if (is.null(venues[[i]]$city)) {venue_data[(p)*20 + i,2] <- "NA"} 
    else {venue_data[(p)*20 + i,2] <- venues[[i]]$city}
    
    if (is.null(venues[[i]]$postalCode)) {venue_data[(p)*20 + i,3] <- "NA"} 
    else {venue_data[(p)*20 + i,3] <- venues[[i]]$postalCode}
    
    if (is.null(venues[[i]]$address$line1)) {venue_data[(p)*20 + i,4] <- "NA"} 
    else {venue_data[(p)*20 + i,4] <- venues[[i]]$address$line1}
    
    if (is.null(venues[[i]]$url)) {venue_data[(p)*20 + i,5] <- "NA"} 
    else {venue_data[(p)*20 + i,5] <- venues[[i]]$url}
    
    if (is.null(venues[[i]]$location$longitude)) {venue_data[(p)*20 + i,6] <- "NA"} 
    else {venue_data[(p)*20 + i,6] <- venues[[i]]$location$longitude}
    
    if (is.null(venues[[i]]$location$latitude)) {venue_data[(p)*20 + i,7] <- "NA"} 
    else {venue_data[(p)*20 + i,7] <- venues[[i]]$location$latitude}
  }
  
  Sys.sleep(0.5)
}

venue_data$longitude <- as.numeric(venue_data$longitude)
venue_data$latitude <- as.numeric(venue_data$latitude)

venue_data$longitude[venue_data$longitude<3.358333 | venue_data$longitude > 7.227778] <- NA
venue_data$latitude[venue_data$latitude< 50.750417 | venue_data$latitude > 53.555] <- NA


venue_data %>% 
  ggplot(aes(longitude,latitude)) +
  geom_polygon(
    aes(x = long, y = lat, group = group), data = map_data("world", region = "Netherlands"),
    fill = "grey90",color = "black") +
  geom_point()+
  theme_void() + coord_quickmap() +
  labs(title = "Event locations across the Netherlands", caption = "Source: ticketmaster.com") +
  theme(title = element_text(size=8, face='bold'),
        plot.caption = element_text(face = "italic"))


```

